The Occurrence of Earth-Like Planets Around Other Stars

### 2014-11-25 paper/kepler-selection.tex
Final edits; as submitted.

\begin{abstract}
  The quantity $\etaearth$, the number density of planets per star per
  logarithmic planetary radius per logarithmic orbital period at one
  Earth radius and one year period, describes the occurrence of
  Earth-like extrasolar planets.  Measurement of $\etaearth$ is
  complicated by the difficulty of detecting Earth-like planets in
  Earth-like orbits about Sun-like stars.  Previous
  estimates\cite{Catanzarite2011,Traub2012,Dong2013,Petigura2013,Foreman-Mackey2014}
  place $1\% \lesssim \etaearth \lesssim 34\%$.  These works dealt
  with the problem of selection effects in the sample by either
  analyzing a region of the period-radius parameter space where
  observations are complete and extrapolating to $R = \REarth$ and $P
  = 1 \mathrm{yr}$\cite{Catanzarite2011,Traub2012}, applying a binned
  analysis incorporating survey incompleteness in the period-radius
  plane\cite{Dong2013,Petigura2013} or analysing the results of a
  customised planet detection pipeline on a subset of the Kepler
  observations\cite{Petigura2013,Foreman-Mackey2014}.  Here we present
  a measurement of $\etaearth$ from a parameterised forward model of the
  (correlated) period-radius distribution and the observational
  selection function in the most recent (Q17) data release from the
  Kepler satellite\cite{Borucki2010,Borucki2011,Batalha2013}.  Our
  data set comprises 181,568 systems observed under the Kepler
  exoplanet observing program (mostly G-type stars on the main
  sequence\cite{Batalha2010}), producing 2598 planetary candidates.
  We parameterise the distribution of planetary periods and radii
  using a single, correlated Gaussian component; treat selection
  effects using a parameterised transit detection probability based on
  the measured noise level and stellar properties in the Kepler
  catalog; and include an empirically-parameterised, independent
  component in the period-radius distribution to represent
  false-positive planet detections.  Using our model we can
  simultaneously estimate $\etaearth$, place constraints on the planet
  period-radius distribution function, and determine the degree of
  contamination by false-positive candidate identifications.  We find
  $\etaearth = \earange$ (90\% CL).  We conclude that each
  star hosts $\rplrange$ planets with $P \lesssim 3 \mathrm{yr}$ and
  $R \gtrsim 0.2 \REarth$, that the peak of the planet radius
  distribution lies at $\Rpeak = \rpeakrange \REarth$, and that $\ln
  P$ and $\ln R$ are correlated with correlation coefficient $r =
  \corrcoeffrange$ (all 90\% CL).  Our empirical model for
  false-positive contamination is consistent with the dominant source
  being background eclipsing binary stars\cite{Fressin2013}, with
  $\fposrange$ (90\% CL) of the candidates being false-positives.  The
  distribution of planets we infer could be the result of a
  highly-stochastic planet formation process producing many correlated,
  fractional changes in planet sizes and orbits.  Our approach of
  determining both the intrinsic distribution of objects and selection
  effects empirically from survey data is generally applicable.
\end{abstract}

>>>>

\begin{abstract}
  The quantity $\etaearth$, the number density of planets per star per
  logarithmic planetary radius per logarithmic orbital period at one
  Earth radius and one year period, describes the occurrence of
  Earth-like extrasolar planets.  Measurement of $\etaearth$ is
  complicated by the difficulty of detecting Earth-like planets in
  Earth-like orbits about Sun-like stars.  Previous
  estimates\cite{Catanzarite2011,Traub2012,Dong2013,Petigura2013,Foreman-Mackey2014}
  place $1\% \lesssim \etaearth \lesssim 34\%$.  These works dealt
  with the problem of selection effects in the sample by either
  analysing a region of the period-radius parameter space where
  observations are complete and extrapolating to $R = \REarth$ and $P
  = 1 \mathrm{yr}$\cite{Catanzarite2011,Traub2012}, applying a binned
  analysis incorporating survey incompleteness in the period-radius
  plane\cite{Dong2013,Petigura2013} or analysing the results of a
  customised planet detection pipeline on a subset of the Kepler
  observations\cite{Petigura2013,Foreman-Mackey2014}.  Here we present
  a measurement of $\etaearth$ from a parameterised forward model of the
  (correlated) period-radius distribution and the observational
  selection function in the most recent (Q17) data release from the
  Kepler satellite\cite{Borucki2010,Borucki2011,Batalha2013}.  Our
  data set comprises 181,568 systems observed under the Kepler
  exoplanet observing program (mostly G-type stars on the main
  sequence\cite{Batalha2010}), producing 2598 planetary candidates.
  We parameterise the distribution of planetary periods and radii
  using a single, correlated Gaussian component; treat selection
  effects using a parameterised transit detection probability based on
  the measured noise level and stellar properties in the Kepler
  catalog; and include an empirically-parameterised, independent
  component in the period-radius distribution to represent
  false-positive planet detections.  Using our model we can
  simultaneously estimate $\etaearth$, place constraints on the planet
  period-radius distribution function, and determine the degree of
  contamination by false-positive candidate identifications.  We find
  $\etaearth = \earange$ (90\% CL).  We conclude that each
  star hosts $\rplrange$ planets with $P \lesssim 3 \mathrm{yr}$ and
  $R \gtrsim 0.2 \REarth$, that the peak of the planet radius
  distribution lies at $\Rpeak = \rpeakrange \REarth$, and that $\ln
  P$ and $\ln R$ are correlated with correlation coefficient $r =
  \corrcoeffrange$ (all 90\% CL).  Our empirical model for
  false-positive contamination is consistent with the dominant source
  being background eclipsing binary stars\cite{Fressin2013}, with
  $\fposrange$ (90\% CL) of the candidates being false-positives.  The
  distribution of planets we infer could be the result of a
  highly-stochastic planet formation process producing many correlated,
  fractional changes in planet sizes and orbits.  Our approach of
  determining both the intrinsic distribution of objects and selection
  effects empirically from survey data is generally applicable.
\end{abstract}
